Blocking-resistant communication\\through domain fronting

### 2015-02-07 docs/fronting.tex
Italics.

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data...},
where ``\textsl{data...}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
an unblockable web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.
\vp{Sketch the limitations of this approach}

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path component of a URL.
For example, in the S3 URL
\urll{https://s3.amazonaws.com/bucketname/filename},
\vp{should ``filename'' in the URL be italicized?  It sounds like it's
a generic placeholder, not a literal}
the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
The path component ``\urll{/bucketname/filename}'',
which would reveal the use of CloudTransport,
cannot be used for blocking because it is encrypted inside HTTPS.

>>>>

A technique known as OSS~\cite{oss} (for
``online scanning service'') bounces messages
through web services that are capable of making HTTP requests.
For example, a censored client may ask an HTTPS-based online translation service to
translate the web page at \urll{http://forbidden.example/}\textsl{data},
where ``\textsl{data}'' is the URL-embedded message the client wants to send.
The translation service requests the URL,
unwittingly sending the message on behalf of the client.
OSS shares certain similarities with domain fronting:
an unblockable web service takes the place of the front domain,
and the destination of the communication is embedded somewhere in an HTTPS query
rather than in the Host header.
\vp{Sketch the limitations of this approach}

@@

CloudTransport~\cite{cloudtransport} uses cloud storage, for example Amazon~S3,
as a communication channel by encoding sends and receives as reads and writes to shared remote files.
CloudTransport has much in common with domain fronting:
it hides the true endpoint of a communication with HTTPS,
and sends traffic through a domain with high collateral damage.
In CloudTransport, the hidden destination, which is a storage bucket name rather than a domain,
is hidden in the path component of a URL.
For example, in the S3 URL
\urll{https://s3.amazonaws.com/}\textsl{bucketname}/\textsl{filename},
the censor only gets to ``see'' the generic domain part, ``\urll{s3.amazonaws.com}''.
The path component ``/\textsl{bucketname}/\textsl{filename}'',
which would reveal the use of CloudTransport,
cannot be used for blocking because it is encrypted inside HTTPS.
